### 2018-06-15 papers/synth/intro.tex
intro line delete

%
VTSs are regulated by the same molecules that they transport.
%
For the purpose of this paper, the VTS molecules we focus on are the transmembrane SNARE proteins.
%
SNAREs drive the recognition of the target compartment by vesicles and
their subsequent fusion.
%
The SNAREs can be divided into v-SNAREs (which are present
on vesicles) and t-SNAREs (which are present on compartments). A
vesicle fuses with a compartment if its v-SNARE can form a complex
with the t-SNARE present on that compartment.
%
Not all v- and t- SNARE combinations can form complexes; this
constraint forms part of the basis for the specificity of vesicle
traffic~\cite{jahn2006snares}.
%
The activity of SNARE proteins is further regulated by their
interaction with other traffic molecules \ashu{ [do we need the following], such as SM
proteins~\cite{sudhof2009membrane} and proteins of tethering
complexes~\cite{hong2014tethering}.}
%

We use the model of VTSs that has been presented
in~\cite{shukla2017discovering}.
%
Please look at Appendix~\ref{sec:model} for a detailed discussion on
pros and cons of the model.
%
We model the system as a labeled graph, where compartments are nodes
and transport vesicles are edges.
%
The molecular compositions of the compartments and vesicles are the
node and edge labels respectively.
%
The molecules can be active or inactive on any a compartment or
vesicle.
%
The activity states of molecules are also included in the labels.
%
Due to the biology of SNAREs of the VTSs our interest, a vesicle is enabled
by a set of {\em four} molecules such that one part of the set occurs in the
vesicle and the other part occurs in the target of the vesicle compartment.
%
The partition is always three and one molecules.
%
% Describe VTS in detail
%Molecules on compartments and on vesicles can be in either an active or an inactive state.
% the term vesicle has already been introduced.. using two terms for the same object seems confusing. 
%
% (The molecules are transported to the other compartments via
%unidirectional channels.) cannot comment on unidirectionality of vesicles. they may be undergoing multiple cycles of back-fusion for all we %know.  
%
%The active molecules regulate the vesicle they occur on.
%
%A vesicle is enabled by a set of molecules such that one part of the set occurs in the vesicle and the other part occurs in the target compartment.
% use either target or destination consistently throughout..i prefer target because that's what the t in t-SNARE stands for.
%
The enabling molecules must be active in the vesicle
and target compartment respectively.
%
The pairs are called {\em fusing} sets and analogously
the vesicle is considered to be {\em fused} with the
destination compartment.
%
Not all sets of molecules can participate in the fusion; in the
biological cells, fusogenic SNARE complexes are discovered through
experiments.
%
%Not all molecule sets can participate in the fusion, the
%potential fusion pairs are usually determined by biological experiments.
%
Generally, the fusing pairs are found to be distinct for distinct vesicle-compartment fusions.
%
To ensure that a molecule that has participated in a fusion does not
interfere with fusion at compartments and vesicles, in the model, we
require that the molecule is inactive on appropriate compartments.
%
The activity of molecules is regulated by the other molecules, i.e.,
the presence and absence of the other molecules in a compartment or
vesicle may make the molecule active or inactive.
%
We call this regulation as {\em activity functions}.
% Defending our model
%
%In this VTS model, we assume that the system is in steady state and the
%concentrations of the molecules in the compartments do not change over
%time.
%
%We model the system as a labelled graph, where compartments are nodes and
%transport vesicles are edges.
%
%The set of molecules present and their activity in a compartment or
%a vesicle is the label of the respective node or edge.
%
The regulation controls are defined by a fusion pairing relation
containing pairs of molecules and activity
Boolean functions.

>>>>

%
VTSs are regulated by the same molecules that they transport.
%
For the purpose of this paper, the VTS molecules we focus on are the transmembrane SNARE proteins.
%
SNAREs drive the recognition of the target compartment by vesicles and
their subsequent fusion.
%
The SNAREs can be divided into v-SNAREs (which are present
on vesicles) and t-SNAREs (which are present on compartments). A
vesicle fuses with a compartment if its v-SNARE can form a complex
with the t-SNARE present on that compartment.
%
Not all v- and t- SNARE combinations can form complexes; this
constraint forms part of the basis for the specificity of vesicle
traffic~\cite{jahn2006snares}.
%
%The activity of SNARE proteins is further regulated by their interaction with other traffic molecules.

%\ashu{ [do we need the following], such as SMproteins~\cite{sudhof2009membrane} and proteins of tethering complexes~\cite{hong2014tethering}. }
%

We use the model of VTSs that has been presented
in~\cite{shukla2017discovering}.
%
Please look at Appendix~\ref{sec:model} for a detailed discussion on
pros and cons of the model.
%
We model the system as a labeled graph, where compartments are nodes
and transport vesicles are edges.
%
The molecular compositions of the compartments and vesicles are the
node and edge labels respectively.
%
The molecules can be active or inactive on any a compartment or
vesicle.
%
The activity states of molecules are also included in the labels.
%
Due to the biology of SNAREs of the VTSs our interest, a vesicle is enabled
by a set of {\em four} molecules such that one part of the set occurs in the
vesicle and the other part occurs in the target of the vesicle compartment.
%
The partition always divides the set in the set of three and one molecules.
%
% Describe VTS in detail
%Molecules on compartments and on vesicles can be in either an active or an inactive state.
% the term vesicle has already been introduced.. using two terms for the same object seems confusing. 
%
% (The molecules are transported to the other compartments via
%unidirectional channels.) cannot comment on unidirectionality of vesicles. they may be undergoing multiple cycles of back-fusion for all we %know.  
%
%The active molecules regulate the vesicle they occur on.
%
%A vesicle is enabled by a set of molecules such that one part of the set occurs in the vesicle and the other part occurs in the target compartment.
% use either target or destination consistently throughout..i prefer target because that's what the t in t-SNARE stands for.
%
The enabling molecules must be active in the vesicle
and target compartment respectively.
%
The pairs are called {\em fusing} sets and analogously
the vesicle is considered to be {\em fused} with the
destination compartment.
%
Not all sets of molecules can participate in the fusion; in the
biological cells, fusogenic SNARE complexes are discovered through
experiments.
%
%Not all molecule sets can participate in the fusion, the
%potential fusion pairs are usually determined by biological experiments.
%
Generally, the fusing pairs are found to be distinct for distinct vesicle-compartment fusions.
%
To ensure that a molecule that has participated in a fusion does not
interfere with fusion at compartments and vesicles, in the model, we
require that the molecule is inactive on appropriate compartments.
%
The activity of molecules is regulated by the other molecules, i.e.,
the presence and absence of the other molecules in a compartment or
vesicle may make the molecule active or inactive.
%
We call this regulation as {\em activity functions}.
% Defending our model
%
%In this VTS model, we assume that the system is in steady state and the
%concentrations of the molecules in the compartments do not change over
%time.
%
%We model the system as a labelled graph, where compartments are nodes and
%transport vesicles are edges.
%
%The set of molecules present and their activity in a compartment or
%a vesicle is the label of the respective node or edge.
%
The regulation controls are defined by a fusion pairing relation
containing pairs of molecules and activity
Boolean functions.
